Temperature Effects on Surface Sulfur Dioxide

### 2011-08-08 Coordination-Results.tex
New plots of the transition graphs, shrank the lifespans, added graphviz citations to the bibtex, and TONS OF TEXT about the coordination results (distro, transitions, lifespans).

The bonding coordination of the surface \suldiox~was determined at each timestep of the simulations. Figure \ref{fig:bonding-coordinations} shows the distribution of bonding coordinations of the surface \suldiox, by percentage of all bonding coordinations encountered, across all the simulations for both the cold (blue) and hot (red) trajectories. A first visual inspection clearly indicates the two most common coordinations: ``S'' and ``SO'', followed by the unbound coordination, and ``SOO''. This trend holds at both temperatures. Also, a \suldiox~configuration with bonds forming solely through the oxygens without any sulfur interactions, or any configuration with more than a single interaction through the sulfur atom are rare in comparison to the single sulfur coordinations. These less common coordinations likely form as transitory configurations when the waters briefly move closer or further away from the surface \suldiox.

The distribution paints a likely picture of the surface adsorption process of a \suldiox~first coming in contact with surface waters. Starting in an unbound state, two methods of initial contact are possible: through the \suldiox-sulfur or through one of the oxygens. Because the population of non-sulfur bonding interactions (not including the ``unbound'' state, i.e. ``O'', ``OO'', ``OOO'', etc.) only account for 3\% of all the configurations sampled, either there is a very brief transition state where the \suldiox~first binds through an oxygen and then quickly adds, or switches to a sulfur interaction with the surface waters, or the first contact is made through the sulfur atom. The ``S'' coordination has a large population, accounting for 35\% of the trajectories in the cold systems, and 32\% in the hot systems. Thus, it is most likely that the first binding contact to the waters is through the \suldiox~sulfur to a water oxygen. Furthermore, once in the ``S'' coordination, the \suldiox~can either unbind, add a second sulfur interaction, or bind through an oxygen. The histogram of Figure \ref{fig:bonding-coordinations} suggests that the preferred route is to further coordinate through an oxygen to achieve the ``SO'' coordination. ``SO'' accounts for 35\% of the cold coordinations, and 36\% of the hot trajectories. Binding to a second oxygen to the ``SOO'' coordination (7\% of the cold, 12\% of the hot systems) is less likely than losing an interaction through an oxygen back to the ``S'' coordination.

@@

We thus have a likely route for adsorption and binding of an unbound \suldiox~to a water surface. The unbound \suldiox~initially binds mostly to a water through the sulfur atom, and then will either unbind, or add an oxygen interaction to oscillate between unbound, ``S'', and ``SO'' coordinations. It may then undergo brief sojourns to other coordinations because of the motions and rearrangements of the surface water molecules. These brief transitory coordinations are overwhelmed by the dominant ``S'' and ``SO'' states. The most probable deviation from those two coordinations is to the ``SOO'', where a second oxygen interaction is formed. Otherwise the \suldiox~unbinds from the surface to repeat the adsorption process.

Baer et al performed this coordination analysis for their single-temperature study, but discriminated between \suldiox~binding through the two different oxygens. They concluded that there is asymmetric hydrogen bonding through the \suldiox~oxygens, with one binding more often than the other. This is supported by the findings here where all the double oxygen coordinations (i.e. ``OO'', ``SOO'', etc.) represent a much lower percentage of the coordinations than the single oxygen counterparts (i.e. ``O'', ``SO'', etc.).

%To further assess the effect of temperature on \suldiox~behavior we turn to analysis of the bonds formed between \suldiox~and the water surface. The bonding coordinations were determined for the \suldiox~based on the bondlength criteria noted in the introduction. Bonds formed between \suldiox-sulfur and \wat-oxygen are labeled 'S' coordinated, and bonds formed between \suldiox-oxygen and \wat-hydrogen are labeled 'O' coordinated. For each bond an additional letter label is appended to the coordination. For example, an 'SOO' coordinated \suldiox~forms three bonds to waters: two bonds are formed through the \suldiox-oxygens, and one through the \suldiox~sulfur. This naming scheme is taken from a similar convention used for describing water bonding interactions, but applied now to the \suldiox~molecule.\cite{Buch2005}

%Figure \ref{fig:so2-bonding-coordinations} shows the distribution of bonding coordinations throughout the set of simulated trajectories for both the cold and hot temperatures. The two most common coordination types are the S and SO, followed by a completely unbound \suldiox~molecule. Bonding is primarily found through the \suldiox-sulfur atom, with higher coordinationsThe distribution shows that the \suldiox~mostly forms one or two bonding interactions with the waters. The bonding of the \suldiox~at both low and high temperatures follows similar trends, however the higher temperature shifts the distribution of coordinations slightly to forming more bonds than the cold temperature \suldiox. Figure \ref{fig:coordination-breakdown} breaks down the coordination distribution to show more details of the \suldiox~interactions.

%The total number of bonds formed to the \suldiox~are shown in the top plot of figure \ref{fig:coordination-breakdown}. The \suldiox~spends more than 70\% of the trajectories forming single or double interactions with surface waters. The center and bottom plots of figure \ref{fig:coordination-breakdown} show the distribution of bonds formed through the \suldiox~sulfur and oxygen atoms, respectively. The sulfur interaction distribution (center) shows the \suldiox~clearly spending most of the simulations forming a single bond through the sulfur atom. This supports the overall distributions heavily weighted by the S and SO coordination types. Looking at the oxygen interaction distribution plot (bottom) of figure \ref{fig:coordination-breakdown}, the oxygen remains mostly unbound or singly bound. By increasing the temperature the amount of unbound oxygen coordinations decreases 10\%, but the increase in the singly bound state is only by 4\%, while the double oxygen interactions increase by 6\% over the colder temperature distribution. Higher temperatures shift the distribution of interactions with \suldiox~to higher coordination types.

%The sfg experiment performed by our group on \suldiox~surface adsorption suggested an SO coordination type based on...\cite{Tarbuck2005,Tarkbuch2006} This was further supported by DFT simulations of single surface \suldiox~molecules bound to water at room temperature.\cite{Baer2010} Our simulations show that the SO interaction type is nearly as prevalent as the single S-type coordination at both temperatures. The colder temperature favors the single bond to the \suldiox~through the sulfur atom more than the high temperature, but the increase in coordination number of the \suldiox~is subtle and does not drastically change with temperature.

% Figure showing all the different types of so2 coordinations
%\begin{figure}[h!]
	%\begin{center}
		%\includegraphics[scale=1.0]{images/coordination/so2-bonding-coordinations.png}
		%\caption{Distribution of bonding coordinations of the surface \suldiox~molecule. Each set of bars represents the amount of time spent in the particular coordination type, including the unbound coordination. The results for the cold (blue) and hot (red) temperatures are shown together. At the high temperature the \suldiox~bonding becomes more complex with more bonds to the sulfur and oxygen atoms. The lower coordination states are more dominated in the cold temperature. The naming scheme is similar to that of a previous scheme for water coordinations,\cite{Buch2005} applied to the \suldiox~molecule.}
		%\label{fig:so2-bonding-coordinations}
	%\end{center}
%\end{figure}

%\begin{figure}[h!]
	%\begin{center}
		%\includegraphics[scale=1.0]{images/coordination/coordination-breakdown.png}
		%\caption{Bonding coordinations of the \suldiox~broken down into specific interactions. The total number of bonds to the molecule (top) are shown regardless of coordination type. The total number of bonds through either the sulfur atom (center) or through both of the oxygens (bottom). The \suldiox~primarily forms one or two bonds to the surface waters. The sulfur atom mostly bonds to a single water oxygen. Between the two \suldiox~oxygen atoms, the molecule mostly does not bond to the water hydrogens, or forms a single hydrogen-bond.}
		%\label{fig:coordination-breakdown}
	%\end{center}
%\end{figure}

@@

The binding behavior of the \suldiox~is altered by changing the temperature of the system, as evidenced in the shift in bonding coordination populations of Figure \ref{fig:bonding-coordinations} from cold to hot. In the cold temperature, the unbound, single oxygen, and ``S'' coordinations are more populated than in the hot systems. We see that the cold \suldiox~spends nearly twice as much time unbound, and only slightly more time in the ``S'' coordination than in the hot system. The increased temperature of the hot systems causes all the coordinations with more than a single sulfur interaction (``SS'', ``SSO'', etc.) to increase over the equivalent cold temperature coordination populations. Most of the unbound population in the hot simulations appears to have shifted to the states with double-oxygen or double-sulfur coordinations. Figure \ref{fig:coordination-breakdown} shows the distribution of the number of bonds through the \suldiox~sulfur (top) and through the \suldiox~oxygens (bottom). When comparing from cold to hot distributions, the change in temperature increases the number of bonds to the \suldiox~sulfur and oxygen atoms. Whereas in the cold system the \suldiox~very rarely forms two interactions through the sulfur, in the hot system we see that the two-sulfur interaction bonding coordination account for nearly 5\% of all coordinations. There is a similar increase in bonding to the \suldiox~oxygens in the hot system. The increased temperature of the hot systems allows the \suldiox to bind to more surface waters than in the cold systems.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-breakdown-small.png}
		\caption{}
		\label{fig:coordination-breakdown}
	\end{center}
\end{figure}

The increased binding through the \suldiox~oxygens at the hot temperatures should have a visible effect on the radial distribution function (RDF) between \suldiox-oxygen and water-hydrogen. Figure \ref{fig:rdf} shows the RDF of the \suldiox~sulfur and oxygen atoms with their water bonding partners, water oxygen and hydrogen, respectively, at both cold (blue) and hot (green) temperatures. Both the first and second peaks of the O$_{SO_2}$-H$_{H_2O}$ RDF increase at the higher temperature, indicating a higher number of water hydrogens near the \suldiox~oxygens in both hydration shells. This corroborates the increased coordination through the \suldiox~oxygens to the surface waters at the higher temperature.

@@

The populations of the single-oxygen coordinations are similar at both temperatures, somewhat contradicting the results of the RDF. We expect an increase of all \suldiox-oxygen interactions with surface water hydrogens at the higher temperature, but the non-sulfur coordinations do not obey this trend. This indicates that the non-sulfur coordinations do not behave as most of the other coordinations, and their small contribution to the overall population in the distribution of Figure \ref{fig:bonding-coordinations} indicates that they are anomalous, or only briefly encountered during the simulations.

The same temperature effect of shifting population to higher bonding coordinations also manifests in the \suldiox~sulfur. The single-``S'' coordinations (``S'', ``SO'', ``SOO'', etc.) have similar populations at both temperatures, but the change from cold to hot temperature shifts the unbound \suldiox~coordinations up towards to the doubly-bound sulfur coordinations (i.e. ``SS'', ``SSO'', etc.). The increased temperature causes more binding to the \suldiox~by allowing for multiple bonds through both the \suldiox~sulfur, and through the oxygens. Thus, the hotter temperature allows for increased coordination of the \suldiox~to the water surface.

When the \suldiox~is on the cold water surface, the ``S'' and ``SO'' coordination populations are nearly equally represented. As the temperature increases to the hot system, the ``S'' coordination decreases, while the ``SO'' increases. We see from the RDFs that colder temperatures favor binding through the \suldiox~sulfur because of the larger first peak in the S$_{SO_2}$-O$_{H_2O}$ RDF. From this increase we expect the ``S''-coordinated \suldiox~to be more prevalent at cold temperatures, as is the case for the coordination distribution. However, the O$_{SO_2}$-H$_{H_2O}$ RDF indicates increased hydrogen bonding through the \suldiox~oxygens at higher temperatures manifested by a larger first peak in Figure \ref{fig:rdf} for the hot temperature. Thus, those \suldiox~bonding coordinations with at least a single bond to an oxygen and to the sulfur, (i.e. ``SO'', ``SSO'', ``SSOO'', etc.) are more prevalent at the high temperature. Overall, we find evidence from both the bonding coordination distribution, and from the RDFs to suggest a modified bonding behavior at different temperatures. At an increased temperature the surface \suldiox~binds more through its oxygens than the cold counterpart. However, like the \suldiox~in the cold temperature, it likely has a persistent interaction through the sulfur atom to a neighboring water oxygen throughout most of the simulated trajectories.

>>>>

The bonding coordination of the surface \suldiox~was determined at each timestep of the simulations. Figure \ref{fig:bonding-coordinations} shows the distribution of bonding coordinations of the surface \suldiox, by percentage of all bonding coordinations encountered for both the cold (blue) and hot (red) trajectories. A first visual inspection reveals several trends in the bonding of the \suldiox. Clearly the ``SO'' coordination is the most populous at both temperatures. The second and third most populated coordinations are the ``S'' and ``SOO'', however the distributions differ between temperatures. In cold simulations the ``S'' and ``SOO'' coordinations occur nearly equally. The hotter temperature simulation shifts the distribution such that the ``S'' occurs 5\% less frequently than in the cold, and the ``SOO'' occurs nearly 10\% more times. The distribution of bonding coordinations in the hot temperature has a clear first and second most frequent coordination: ``SO'' and ``SOO'', respectively. These results for the hot (room temperature) system coincide with those of the previous single-temperature simulation study by Baer et al. at a similar temperature.\cite{Baer2010}

@@

	Several conclusions about the bonding behavior of \suldiox~to surface waters stem from the distribution of coordinations. Clearly the cold \suldiox~spends more time than the hot \suldiox~(10\%) completely unbound from the surface waters. This does not necessarily imply a complete desorption into the gas phase, but only a brief sojourn away from the waters, with all interactions and bond lengths longer than the cutoff criteria set for the analysis. Furthermore, the most frequently occuring bonding coordinations are ``S'',``SO'', and ``SOO'', with ``SO'' being the most populated at both temperatures. Baer et al. also concluded that these three coordinations werethe most frequent for a room temperature simulation, and specifically isolated the ``SO'' and ``SOO'' as most common in their study.\cite{Baer2010}

	Looking closer at the coordination types it is notable that coordinations lacking any sulfur interactions (i.e. ``O'', ``OO'', etc.) represent the least formed bonding coordinations. A bonding coordination with at least a single sulfur interaction is clearly favored over \suldiox~oxygen-only bonding to waters. In our previous classical simulations of \suldiox~on water we concluded that during adsorption and throughout the interface, the \suldiox-sulfur points further into the \wat~bulk than the oxygens.\cite{Shamay2011} The coordination distributions here support the idea that binding through the sulfur is preferable, and to the extent that a non-sulfur coordination is rarely formed during the course of all our simulations.

% Baer's assymetric oxygen binding
Baer et al performed this coordination analysis for their single-temperature study, but discriminated between \suldiox~binding through the two different oxygens. They concluded that there is asymmetric hydrogen bonding through the \suldiox~oxygens, with one binding more often than the other. This is supported by the findings here where all the double oxygen coordinations (i.e. ``OO'', ``SOO'', etc.) represent a much lower percentage of the coordinations than the single oxygen counterparts (i.e. ``O'', ``SO'', etc.). Furthermore, a triple-oxygen coordination (i.e. ``OOO'', ``SOOO'', etc.) is very rarely encountered. Three \suldiox~oxygen bonds only form if both \suldiox~oxygens are interacting with water hydrogens. Our finding that triple-oxygen coordinations rarely form complements Baer et al's conclusion about the assymetry in the oxygen interactions.

Having established the preference for an interaction through the \suldiox~sulfur atom, we look to the right side of Figure \ref{fig:bonding-coordinations} at the double-sulfur coordinations (i.e. ``SS'', ``SSO'', ``SSOO'', etc.). We see from the datat that single-sulfur coordination are overwhelmingly preferred over double-sulfur ones. Also, adding a third oxygen atom is also unfavorable as the ``OOO'' and ``SSOOO'' coordinations are almost completely unrepresented (less than 1\%), and the change from ``SOO'' to ``SOOO'' produces a very large drop in the coordination distribution of Figure \ref{fig:bonding-coordinations}.

We can now form a picture of a typical \suldiox~molecule adsorbed to a water surface across both temperatures in this study. The \suldiox~will have at least one interaction to neighboring waters through the sulfur, and will then bond assymetrically through one of the oxygens either once or twice to water hydrogens. The \suldiox~oxygen bonds will form and break throughout a trajectory, and overall the most dominant coordination will be the ``SO'' bonding arrangement.

@@

The binding behavior of the \suldiox~is altered by changing the temperature of the system, as evidenced in the shift in bonding coordination populations of Figure \ref{fig:bonding-coordinations} from cold to hot. In the cold temperature, the unbound, ``S'', and ``SO'' coordinations are more populated than in the hot systems. The increased temperature decreases the time spent unbound to the surface waters, and causes all the coordinations to the right of ``SO'' in Figure \ref{fig:bonding-coordinations} to increase over the equivalent cold temperature coordination populations. We see that the cold \suldiox~spends nearly four times as much time unbound as the hot \suldiox, with most of the unbound population in the hot simulations shifting to the stateswith double-oxygen and double-sulfur coordinations.

On the cold water surface, the ``S'' and ``SO'' are more populated than for the hot system. The relative decrease of these coordinations are matched in the hot surface by an increase of the ``SOO'' configuration. This speaks to a dramatic difference in the surface behavior of \suldiox~at the two temperatures. The cold \suldiox~spends nearly equal time between the ``S'' and ``SOO'' coordinations, but nearly 20\% more time in the ``SO''. Thus the addition, or removal of a bond through the \suldiox-oxygen is equally probable, as long as the pivotal sulfur interaction remains intact. Figure \ref{fig:rdf} shows the radial distribution functions (RDF) of \suldiox~to water atoms for both cold (blue) and hot (red) temperatures. The \suldiox-S to \wat-O RDFs are nearly equal except for a slightly taller first peak of the cold system. Along with the slightly larger population of the cold ``S'' and ``SO'' coordinations in the cold surface, the RDF would indicate that with bonding mostly through the sulfur, the cold \suldiox-sulfur interacts more closely with the surface waters. As the temperature increases in the hot system, the added bonding through a second oxygen interaction may be pulling the bonding waters further from the \suldiox-sulfur. This suggests that the cold \suldiox~bonds to water's surface more through its sulfur atom (as shown in the \suldiox-S RDF) and favors the more sulfur-centric bonding coordinations (i.e. ``S'', ``SO''). The increased temperature allows the \suldiox~to bond more extensively through its oxygens to the ``SOO'' coordination. In turn, the increase binding through the oxygens may pull the \suldiox~further into the water interface and then allow for increased brief bonding through the sulfur, up to double-sulfur coordinations (i.e. ``SS'', ``SSO'', etc.).

@@

\subsection {Bonding Transitions}

During the course of each simulation, the \suldiox~bonding coordination was determined and recorded for each timestep. From the coordination data we extract not only the populations of the various bonding coordinations encountered, but also the frequencies of transitions between the different coordinations (i.e. the number of times an \suldiox~switched from one coordination type to another). With this data we have generated the directed graphs of Figure \ref{fig:coordination-transitions} depicting the cold and hot (Figure \ref{fig:coordination-transitions} A and B, respectively) bonding coordinations as circular colored nodes.\cite{Ellson2004,Gansner1999} The transitions between the coordinations are depicted as directed edges pointing in the direction of the transition from one coordination to another. The populations of the coordinations are depicted by both the node size and coloration (larger and darker red coordinations occur more frequently). Populations of the transitions between coordinations are depicted by arrow thickness, with thicker lines corresponding to more frequently occuring transitions. Additionally, the transition lines are numbered to the right of each line with the number of times each transition occured. Only the most populated nodes and transitions between them are shown. This accounts for the difference of inbound and outbound nodes to certain nodes not equalling zero, as would happen for a complete graph representation of all coordinations and transitions.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-transitions.png}
		\caption{}
		\label{fig:coordination-transitions}
	\end{center}
\end{figure}

As expected for the more populated coordinations, there are more transitions between larger nodes in Figure \ref{fig:coordination-transitions} than transitions to less populated coordinations. However, some insights to the bonding process are made clearer from these graphs. In the cold system graph of Figure \ref{fig:coordination-transitions}A, we find that the majority of transitions are between the ``S-SO'' and ``SO-SOO'' nodes. The number of transitions within this ``S-SO-SOO'' cluster of coordinations is an order of magnitude larger than any other transition. This indicates that while the \suldiox~is bound in any of the three most populated bonding coordinations, it is actively binding and unbinding the oxygens to form the other two coordinations in this group. The \suldiox~is rather active and constantly forming and breaking bonds to with its oxygens.

In the graph of the hot system in Figure \ref{fig:coordination-transitions}B, the transition frequencies follow the same trend as in the cold system, increasing with adjacent node size. One very surprising result is in the transition from ``SOO-SOOO''. The transition frequency does not follow from the adjacent node sizes, as the ``SOOO'' node represents less than 5\% of the bonding coordinations. This is indicative of a very rapid cycle of forming and breaking of bonds to the second \suldiox~oxygen. As noted earlier, it is likely that the ``SOO'' \suldiox, assymetrically binding twice through a single oxygen, is pulled further into the water interface. It is likely more surrounded by waters, and in the hot system it can often form a brief third hydrogen bond to a water through the second \suldiox~oxygen. Because the triple-oxygen coordination is not as favorable, it quickly breaks the bond and the \suldiox returns back to the ``SOO'' coordination.

Given the information we have about the frequencies of bonding coordination transitions, it is possible to draw a likely route of adsorption beginning with an unbound \suldiox. From the unbound state, the \suldiox~can bind to waters either through the sulfur or an oxygen to enter the ``S'' or ``O'' coordinations, respectively. At both temperatures we find that the coordination transition in Figure \ref{fig:coordination-transitions} from unbound to ``O'' occurs almost three times more than the transition from unbound to ``S''. Either the ``O'' state is more easily formed, but also quickly broken, accounting for the higher transition frequency, or the ``O'' coordination is in fact the first step in adsorption of the unbound \suldiox, leading to a transition to the most frequent coordination, ``SO'', through addition of an \suldiox~sulfur interaction to a water oxygen.

To verify the claim that the ``O'' coordination forms from, and breaks quickly to the unbound state as is suggested by the transition frequency plots in Figure \ref{fig:coordination-transitions}, rather than enduring longer, we plot the lifespans of the various coordinations in Figure \ref{fig:coordination-lifespans}. Each point in the plot represent a time during the simulated trajectories in which the \suldiox~formed the respective coordination. The vertical ``lifespan'' position is calculated directly from the amount of time spent in the given coordination before changing to another. Both cold (blue) and hot (red) simulation data are plotted. The data of Figure \ref{fig:coordination-lifespans} show that most coordination configurations last a very brief time, with the majority forming for under 0.5 ps. The three most populous coordinations, ``S'', ``SO'', ``SOO'' (as determined from Figure \ref{fig:bonding-coordinations} by percentage) in both temperatures have coordination lifetimes of up to 1 ps, in some instances lasting up to 1.5 ps. The brevity of the lifespans overall speaks to the dynamic nature of the interface. The length of time in each coordination parallels the populations of the coordinations, and suggests an ordering of stabilities of the various bonding coordinations. The ``unbound'' configuration stands out as an anomaly amonst the lifespans of the other bonding coordinations. The few data points above 1.5 ps, up to 3.25 ps long, suggest a \suldiox~that not only unbinds from the water surface, but also detaches far enough to avoid the quick rebinding and coordination change to ``S'' or ``O''. Those few long lived unbound data points indicate times when the \suldiox~is far from the water, residing in the gas phase until the necessary water rearrangement  has drawn it back to the surface to rebind.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-lifespans.png}
		\caption{}
		\label{fig:coordination-lifespans}
	\end{center}
\end{figure}

Returning now to the transition plots of Figure \ref{fig:coordination-transitions}, the behavior of the unbound transition to both ``S'' and ``O'' states can now be better characterized. Figure \ref{fig:coordination-lifespans} shows that the ``O'' state lifetimes are shorter than the ``S'' coordinated \suldiox. Figure \ref{fig:coordination-transitions} shows that the unbound-``O'' transition occurs almost three times more than the transition to the ``S''. Thus the unbound \suldiox~forms a bond to a neighboring water through its oxygen, but that bond is short-lived and quickly breaks sending the \suldiox~back to being unbound, or it transitions to the ``SO'' state by forming another bond through the sulfur. The unbound-``S'' transition does not occur as often because the ``S'' state is likely more stable than the ``O''. Once in the ``S'' coordination the \suldiox~does not quickly break the interaction from its sulfur to water, but rather remains for up to 1 ps in the ``S'' coordination before most likely forming an oxygen bond to make the ``SO'' coordination. We have outlined the likely behavior of \suldiox~as it transitions from the unbound state to binding with surface waters.

Once the \suldiox~is bound to the water surface, the pathway leading back to the unbound state is not often traversed. As shown in Figure \ref{fig:coordination-transitions} the dominant coordination transitions occur between the cluster of ``S-SO-SOO'' coordination nodes. This suggests that the \suldiox~sulfur interaction to a water oxygen has a much longer lifespan than the oxygen bonding to water hydrogens. The difference between the ``S-SO-SOO'' coordinations is an addition of oxygen bonds, and the frequent transitions show that the bonds to \suldiox~oxygens are quickly forming and breaking. For the \suldiox~sulfur interaction to break, the \suldiox~must enter a non-sulfur coordination (i.e. ``O'', ``OO'', unbound, etc.) or a coordination with more than a single sulfur interaction (i.e. ``SS'', ``SSO'', etc.). The transitions to coordinations that allow for breaking of the \suldiox~sulfur interactions, or switching the interaction to another water, are infrequent compared to those leading to an oxygen bond transition. Thus, the \suldiox~spends most of its time while bound to the surface waters breaking and forming hydrogen-bonds through its oxygens, and interacting with neighboring waters through a more persisten interaction via the \suldiox~sulfur atom.
